Data Provenance Tracking for Concurrent Programs

### 2014-11-15 paper.tex
add acks section

>>>>

\section*{Acknowledgements}

We would like to thank our anonymous reviewers for their invaluable comments.
Our thanks also to Kathryn McKinley and the members of the Sampa group at the University of Washington.
This work was supported in part by C-FAR, one of six centers of STARnet, a
Semiconductor Research Corporation program sponsored by MARCO and DARPA.
It was also supported by a gift from Google.
